Large squeezing in multicomponent trapped Bose-Einstein condensates

### 2012-12-07 large_number_squeezing_with_atoms.tex
Add realistic squeezing figure to paper

>>>>

Taking all the lessons learned, we can get good squeezing for realistic paramters in 3D. Figure \ref{figXXX} shows an example of a full 3D simulation, 10000 paths, box potential in 2d, tight trapping (1500Hz) in the 3rd dimension.
\begin{figure}
  \centering
   \includegraphics[width=7cm]{figures/realistic_3d_squeezing_params.eps}
\caption{Full 3D simulation of relative number squeezing in state $|a\rangle$ in a system with realistic parameters. Box potential in two dimensions with area 120$\mu$m $\times$ 120$\mu$m, tight harmonic trapping in 3rd dimension with $\omega=1500$Hz. Solid red line, analytic 0D solution; dashed blue line, full 3D multimode simulation. Parameters: Rb$^{85}$ atoms, $n_a = n_b =2 \times 10^5$, $U_{aa}=2.1\times 10^{-50}$ (corresponding to an s-wave scattering length of $-400 a_0$), $U_{bb}=U_{ab}=0$, $\tau_{\mathrm{hold}}=1\times 10^{-3}$s, $\phi=5.3$. Even with all multimode effects present, the number squeezing in the 3D system (13.9dB) approaches that of the ideal 0D case (15.1dB).}
 \label{figRealistic3DParameters}
\end{figure}
